Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-06-15 ms.tex
adding tau scaling plot to paper for steady state solution
changing colorscheme of tau and xinit three panel plots
Added definition of change of frequency variables in the derivation of the steady state solution

\subsection{Derivation of the Steady-State Solution}
Now, consider a sphere of radius $R$ and uniform density, with line-center optical depth $\tau_0 = (k/\sqrt{\pi}\Delta)R$. Here, the Doppler width is $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light. After changing the photon frequency variable in Eq. \ref{eq:rteqn} and performing all angular integrals, we obtain Eq. \ref{eq:finaleqn} (see Appendix \ref{app:rteqn_derivation}) and set $p=\alpha_{\rm abs}=0$ to eliminate photon destruction terms. With a photon emission term given by Eq. \ref{eq:jem}, this gives the transfer equation
\be
\nabla^2 J + \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J}{\partial \sigma^2} & = & 
- \frac{ \sqrt{6} kL}{4\pi \Delta^2} \delta^3(\vec{x} - \vec{x}_s) \delta (\sigma - \sigma_{\rm s})
\label{eq:rt_no_destr}
\ee
where the form of the source term is in Eq. \ref{eq:jem_v2}. The boundary condition is that there is no incoming flux at the surface, which can be written
\citep{1986rpa..book.....R}
\be
J & = & \sqrt{3} H
\label{eq:bc}
\ee
at $r=R$.

@@

 \begin{figure}
    \centering
    \includegraphics{threepanel_test.png}
    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$. Photons are initialized with $\rm x = 0.0, 6.0, 12.0$ to examine the solutions' accuracy with a changing source frequency. TODO: Remove blue line. We really don't care about the divergent solution anymore.} 
    \label{fig:sol_mc_xinit}
\end{figure}

 \todo{
 TODO: Add optical depth comparison figure, $x_s$ comparison figure
}

>>>>

\subsection{Derivation of the Steady-State Solution}
Now, consider a sphere of radius $R$ and uniform density, with line-center optical depth $\tau_0 = (k/\sqrt{\pi}\Delta)R$. Here, the Doppler width is $\Delta = \nu_0 v_{\rm th}/c$, where $v_{\rm th}=\sqrt{2k_{\rm B}T/m_{\rm H}}$ is the thermal speed of hydrogen atoms of mass $m_{\rm H}$ and temperature $T$, and $c$ is the speed of light. After changing the photon frequency variable in Eq. \ref{eq:rteqn} and performing all angular integrals, we obtain Eq. \ref{eq:finaleqn} (see Appendix \ref{app:rteqn_derivation}) and set $p=\alpha_{\rm abs}=0$ to eliminate photon destruction terms. With a photon emission term given by Eq. \ref{eq:jem}, this gives the transfer equation
\be
\nabla^2 J + \left( \frac{k}{\Delta} \right)^2 \frac{\partial^2 J}{\partial \sigma^2} & = & 
- \frac{ \sqrt{6} kL}{4\pi \Delta^2} \delta^3(\vec{x} - \vec{x}_s) \delta (\sigma - \sigma_{\rm s})
\label{eq:rt_no_destr}
\ee
where the form of the source term is in Eq. \ref{eq:jem_v2} and a change of variables in frequency has been performed using $d\sigma/dx = \sqrt{2/3}\ \phi(x)^{-1}$. The boundary condition is that there is no incoming flux at the surface, which can be written
\citep{1986rpa..book.....R}
\be
J & = & \sqrt{3} H
\label{eq:bc}
\ee
at $r=R$.

@@

 \begin{figure}
    \centering
    \includegraphics{xinit_threepanel.pdf}
    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$. Photons are initialized with $\rm x = 0.0, 6.0, 12.0$ to examine the solutions' accuracy with a changing source frequency. TODO: Remove blue line. We really don't care about the divergent solution anymore.} 
    \label{fig:sol_mc_xinit}
\end{figure}

 \begin{figure}
    \centering
    \includegraphics{tau_threepanel_factorof2.pdf}
    \caption{Increasing the line center optical depth. Shown here are $\tau_0 = 10^5, 10^6, 10^7$ with the $x$ and $y$ axes scaled by the characteristic frequency diffusion scale $(a\tau_0)^{1/3}$. Photons are initialized with $\rm x = 0.0$.} 
    \label{fig:sol_mc_tau}
\end{figure}
